The Astropy Project: \\ Sustaining and Growing a Community-oriented Open-source Project and the Latest Major Release (v5.0) of the Core Package

### 2022-03-23 src/ms.tex
Clarify future asdf support
Co-authored-by: William Jamieson <wjamieson@stsci.edu>

\astropy now supports reading and writing tables in the American Astronomical
Society Journals' Machine-Readable Table (\href{https://docs.astropy.org/en/stable/io/ascii/write.html#cds-mrt-format}{MRT}) format. This ASCII format has
long been missing and was added to \astropyTable\ I/O in a Google Summer of Code 2021 project.
In addition, \astropyTable\ may also read from and write
to \href{https://asdf-standard.readthedocs.io/en/latest/}{ASDF},
\href{https://docs.astropy.org/en/stable/io/unified.html#table-io-parquet}{Parquet},
and \href{https://wwwastro.msfc.nasa.gov/qdp/}{QDP} formats.

>>>>

\astropy now supports reading and writing tables in the American Astronomical
Society Journals' Machine-Readable Table (\href{https://docs.astropy.org/en/stable/io/ascii/write.html#cds-mrt-format}{MRT}) format. This ASCII format has
long been missing and was added to \astropyTable\ I/O in a Google Summer of Code 2021 project.
In addition, \astropyTable\ may also read from and write
to \href{https://asdf-standard.readthedocs.io/en/latest/}{ASDF},\footnote{Starting in v5.1,
direct \astropypkg support for ASDF has been deprecated in favor of moving it
to the new \package{asdf-astropy} \citep{asdf-astropy} package to accommodate
the differing release schedules between ASDF and \astropypkg.}
\href{https://docs.astropy.org/en/stable/io/unified.html#table-io-parquet}{Parquet},
and \href{https://wwwastro.msfc.nasa.gov/qdp/}{QDP} formats.
